Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-05 doc/main_jfm.tex
updates

\begin{equation}
b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_\Sigma R \dot\theta dS}.
\end{equation}

\begin{table}[ht] 
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\dot\gamma$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

@@

%\begin{figure}
%\centering
%\includegraphics[height=1.2in]{N116_cont_a.pdf}
%\includegraphics[height=1.2in]{N116_cont_b.pdf}
%\includegraphics[height=1.2in]{N116_cont_c.pdf}
%\includegraphics[height=1.2in]{N116_cont_d.pdf}
%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
%  }
%    \label{figure8}
%\end{figure}

@@

>>>>

The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
slip velocity. This quantity is given by 
\begin{equation}
b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_{\Sigma_M} R \dot\theta dS}.
\end{equation}
%
where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.

@@

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\dot\gamma$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

@@

\section{\label{A2} Comparison between Continuum Model and the Proposed Model}

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_cont_a.pdf}
\includegraphics[height=1.2in]{N116_cont_b.pdf}
\includegraphics[height=1.2in]{N116_cont_c.pdf}
\includegraphics[height=1.2in]{N116_cont_d.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
  }
    \label{figureB}
\end{figure}
